\begin{acknowledgements}
I am immensely grateful to my advisor Yaser Sheikh who has been an ideal mentor and teacher for me. Without his encouragement, guidance, and mentorship, none of this work would be possible. I also greatly appreciate my thesis committee - Takeo Kanade,  Louis-Philippe Morency, David Forsyth, and Mina Cikara for their valuable feedback and advice.

I would like to thank Hyun Soo Park who guided me at the beginning of my PhD and has been a mentor throughout the years. I've been fortunate to have many great collaborators in materializing the Panoptic Studio: Tomas Simon, Xulong Li, Hao Liu, Lei Tan, Lin Gui, Sean Banerjee, Timothy Godisart, Bart Nabbe, Iain Matthews, and Shohei Nobuhara. I also thank all of our current and previous group members: Minh Vo, Aayush Bansal, Varun Ramakrishna, Yair Movshovitz-Attias, Natasha Kholgade Banerjee, Donglai Xiang, Gines Hidalgo, Shih-En Wei, Zhe Cao, Luona Yang, Gaku Nakano, Xiu Li, Raaj Yaadhav, and Haroon Idrees. I've been also fortunate to collaborate with Thabo Beeler, Derek Bradley, and Chenglei Wu during my internship at Disney Research Zurich. I am also grateful to many researchers at Facebook Reality Labs Pittsburgh for their advice and feedback during my internship. I would like to express my great appreciation to Jessica Hodgins, Chris Atkeson, Kris Kitani, Srinivasa Narasimhan, Abhinav Gupta, Simon Lucey, Deva Ramanan, Fernando De la Torre, John O’brien, Nancy Pollard, Jim McCann, and Martial Hebert for many insightful discussions, help, and advice.

I would like to especially thank my family - my parents, parents-in-law, my brother, brothers-in-law for their love, support, and encouragement. Last, but not least, I dedicate this thesis to my beloved wife, Sooyeon Lee, and our children, Ian and Erin, for their tireless love, support, and sacrifices. 
\end{acknowledgements}